Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-05 paper/disc20clustering.tex
wip

First, we construct a ground set of size $k-1$ on one of the clusters $S$.
This, way, in any configuration, there exists an alone node that accompanies it.
In such setting, we only issue requests between the current alone node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, \OPT performs one migration.

@@

	We claim that expanding ground sets in this way can continue as long as at least $\ell$ alone node exists.
	Fix the moment just before the creation of a ground set with the node $x_i$.
	We show that if at least $\ell$ alone nodes exists (including $x_i, y_i$), then there exists a perfect partition of ground sets.

>>>>

First, we construct a ground set of size $k-1$ on one of the clusters $S$.
Then, in any configuration, there exists an alone node on $S$.
In such setting, we only issue requests between the current alone node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, \OPT performs one migration.

@@

	We claim that expanding ground sets in this way can continue as long as at least $\ell$ alone node exists.
	Fix the moment just before the creation of a ground set with the node $x_i$.\maciek{no $x_i$ def any more}
	We show that if at least $\ell$ alone nodes exists (including $x_i, y_i$), then there exists a perfect partition of ground sets.
